Convolutional Neural Networks and Volcano Plots: Screening and Prediction of Two-Dimensional Single-Atom Catalysts for CO\textsubscript{2} Reduction Reactions

### 2024-01-15 paper/arxiv/main_3_introduction.tex
move into arxiv dir
format fixes
revise figure captions

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.95\linewidth]{main_fig1_pipeline.png}
    \caption{\textbf{Catalyst Performance Analysis Pipeline Integrating Volcano Plots and CNN.}
    The figure demonstrates the integrated usage of volcano plots for
    predictive assessments of existing catalysts and the utility of CNNs
    to predict and modulate adsorption energies \(E_{\text{ads}}\) using eDOS as input.
    Advanced occlusion and shifting experiments on eDOS are conducted to extract chemical meanings from CNN model.}
    \label{main_fig1:pipeline}
\end{figure}

>>>>

% Figure 1: Catalyst Performance Analysis Pipeline
\begin{figure}[htbp]
    \centering
    \includegraphics[width=\textwidth]{main_fig1_pipeline.png}
    \caption{\textbf{Catalyst Performance Analysis Pipeline Integrating Volcano Plots and CNN.}
    The figure demonstrates the integrated usage of volcano plots for
    predictive assessment of existing catalysts, and the utility of CNNs
    to predict and modulate adsorption energies \(E_{\text{ads}}\) using eDOS as input.
    eDOS occlusion and shifting experiments are conducted to extract chemical information from CNN model.}
    \label{main_fig1:pipeline}
\end{figure}

### 2024-01-15 paper/arxiv/main_4.2_volcano_plots.tex
revise figure captions

% Figure 3: Limiting Potential Volcano Plot and Periodic Table
\begin{figure}[htbp]
    \centering
    \includegraphics[width=\textwidth]{main_fig3_volcano.png}
    \caption{\textbf{Limiting Potential Volcano Plot and Periodic Table.}
    \textbf{a}. Limiting potential volcano plot computed from hybrid-descriptor-based
    linear scaling relations at -0.17 V vs SHE.
    In the plot, the circle, triangle, square, diamond, plus, and star symbols represent metals supported on g-C\textsubscript{3}N\textsubscript{4}, nitrogen-doped graphene, graphene with dual-vacancy, black phosphorous, BN, and C\textsubscript{2}N, respectively.
    Dotted purple lines delineate regions representing rate-determining steps (RDS), with roman numerals denoting the respective RDS for each region.
    \textbf{b}. Limiting potential periodic table illustrating the theoretical activity of
    single atom catalysts, where metals are supported on g-C\textsubscript{3}N\textsubscript{4}.}
    \label{main_fig3:volcano}
\end{figure}

>>>>

% Figure 3: Limiting Potential Volcano Plot and Periodic Table
\begin{figure}[htbp]
    \centering
    \includegraphics[width=\textwidth]{main_fig3_volcano.png}
    \caption{\textbf{Limiting Potential Volcano Plot and Periodic Table.}
    \textbf{a}. Limiting potential volcano plot computed from hybrid-descriptor-based
    linear scaling relations at potential of -0.17 V vs SHE.
    In the plot, the circle, triangle, square, diamond, plus, and star symbols represent
    metals supported on g-C\textsubscript{3}N\textsubscript{4}, nitrogen-doped graphene,
    graphene with dual-vacancy, black phosphorous, BN, and C\textsubscript{2}N, respectively.
    Dotted purple lines delineate regions representing rate-determining steps (RDS),
    with roman numerals denoting the respective RDS for each region.
    \textbf{b}. Limiting potential periodic table illustrating the theoretical activity of
    single atom catalysts supported on g-C\textsubscript{3}N\textsubscript{4}.}
    \label{main_fig3:volcano}
\end{figure}
